\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist 

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{booktabs}
\usepackage{tabularx}

\usepackage{amsmath}
\usepackage{amstext}

\definecolor{bluecolor}{rgb}{0.16,0.16,0.16}

% adjust the page margins
\usepackage[scale=0.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Bollapragada}{Naga Ratna Kumar}
%\title{Resumé title}                               % optional, remove / comment the line if not wanted
\address{$Dr. No. \#$376, Lane No. 3, Netaji Nagar, Pimple Gurav}{Pune 411061}% optional, remove / comment the line if not wanted; the "postcode city" and and "country" arguments can be omitted or provided empty
\phone[mobile]{+91~8830994539}                   % optional, remove / comment the line if not wanted
\phone[mobile]{+91~9494668151}                    % optional, remove / comment the line if not wanted
%\phone[fax]{+3~(456)~789~012}                      % optional, remove / comment the line if not wanted
\email{ngratnakumar@outlook.com}                     % optional, remove / comment the line if not wanted
%\homepage{http://ratna.branded.in}               % optional, remove / comment the line if not wanted
%\extrainfo{https://in.linkedin.com/in/ratna-kumar-b-n-53853168} % optional, remove / comment the line if not wanted
%\homepage{http://home-akshatsingh.rhcloud.com/aks/}
%\photo[45pt][0.4pt]{akshat}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file

\quote{To apply the existing abilities & skills upto the fullest satisfaction of the authorities that will allow myself to take full advantage of my passion and experience in software engineering & computer science and evolve along with the organization.}
%\quote{Use my skills and knowledge for daily monitoring, development and maintenance of mission critical production infrastructure in a hi-tech environment with committed $\&$ dedicated people, which will help me to explore myself fully and realize my potential.} 
                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                                           
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother
%\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}% CONSIDER REPLACING THE ABOVE BY THIS

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\makecvtitle
\section{Professional Qualification}
%\cventry{2009--2010}{PGDIT}{Indian Institute of Information Technology and Management - Kerala}{Thiruvananthapuram with an overall CGPA of}{\textit{9.31}}{}  % arguments 3 to 6 can be left empty
\cventry{2009--2013}{B.Tech - Computer Science}{Pydah College of Engineering and Technology}{Visakhapatnam affiliated to JNTU Kakinada}{\textit{}}{}
~\\
\section{Professional Summary}
\begin{itemize} 
\item Overall 5+ years of industrial rich IT experience in various domains and technologies..
\item 3+ years working in Astronomy Domain developing tools and software integration.
\item Experience in Server administration, Documentation and automation of tasks.
\item Configured Customized cluster for processing Astronomical Data and generating Images using SPAM(Source Peeling and Atmospheric Modeling).
%\item Involved in Debian packaging for a new Debian distribution \textit{Debian-Astro} dedicated for Astronomy and Astrophysics.
\item Involved in the promotion of Free and Open Source Software and participated conferences and workshops on various computing topics across India.
\end{itemize}
~\\
\section{Systems Skills}
\begin{itemize}
\item Developing Astronomical Image Processing pipelines and utilities, along with Unix and Python scripts to integrate the various astronomy tools and software .
\item Experience in AIPS (Astronomical Image Processing System) and Python Astronomy Libraries (astropy.io, scipy, PyBDSF) 
\item Experience in dealing with LTA (Long Term Archive) and FITS (Flexible Image Transport System)
\item Installation and configuration of Linux operating systems like CentOS, Red Hat, Debian, Ubuntu, Fedora with dual booting.
\item Managing groups and user accounts assigned permissions to users using LDAP.
%\item Hands on expertise in building OpenShift applications.
%\item Configuring Linux Kernel recompilation as per need.
\item Disk Management and partitioning in Linux Systems.
%\item Installing the device drivers for all the external and internal devices.
%\item Configuring and implementing network file system protocols.
\item Configuring and implementing Web servers Apache, Tomcat, Glassfish and Zope.
\item Configuring and implementing of version control like Subversion, Git and integrating with Bug Tracking
System (Trac) and Apache webserver.
%\item Configuring mail server using postfix.
%\item Configuring Hadoop cluster from scratch.
\item Automating the repeated processes using Shell Scripts and Python and configuring with Cron jobs for taking automated backups of the system.
\item Working with admin tools like webmin, top, ping.
%\item Installation and Management of CMS like Plone/Zope, Moodle, Wiki and integration with LDAP.
\item Installing all the software applications through package manager, repository or source for Linux/Mac.
\end{itemize}
\pagebreak
~\\
\section{Software Skills}
% Please add the following required packages to your document preamble:
% \usepackage{booktabs}
\begin{center}
\centering
\label{my-label}
\cvitem{}{\begin{itemize}{\textbf{Languages : }}
	\item Python Scripting,
	\item Basic Java
\end{itemize}}
\cvitem{}{\begin{itemize}{\textbf{Scripting Languages : }}
	\item Shell Scripting,
	\item PHP
\end{itemize}}
\cvitem{}{\begin{itemize}{\textbf{Databases : }}
	\item PostgreSQL,
	\item MySQL
\end{itemize}}
\cvitem{}{\begin{itemize}{\textbf{WebServer : }}
	\item Apache Tomcat,
	\item Apache/httpd,
	\item Glassfish
\end{itemize}}
\cvitem{}{\begin{itemize}{\textbf{Tools : }}
	\item LaTEX,
	\item Libre Office,
	\item Trac,
	\item vim,
	\item PyCharm,
	\item WIKI,
	\item GIT/SVN	
\end{itemize}}
~\\
\section{Operating Systems}
\cvitem{}{\begin{itemize}
    \item Ubuntu 8.04 onwards
    \item RHEL 7.0 , Centos 6.x, 7.0
    \item Fedora 18 onwards
	\item Mac X Mavericks onwards
	\item Windows XP onwards
\end{itemize}}
~\\
\section{Open Source Libraries}
\cvitem{}{\begin{itemize}
    \item OpenLDAP
    \item OpenCV
	\item FFMPEG
	\item Docker
	\item SPAM - Source Peeling and Atmospheric Modeling
\end{itemize}}

~\\
\section{Work Experience}
\subsection{National Centre for Radio Astrophysics – Tata Institute of Fundamental Research, Pune \-\ (http://www.ncra.tifr.res.in)}
\cventry{September 2015 -- till date}{Project Engineer}{National Centre for Radio Astrophysics – Tata Institute of Fundamental Research}{Pune}{}{National Centre for Radio Astrophysics – Tata Institute of Fundamental Research (NCRA-TIFR), Pune is a leading centre of research under the umbrella of \textit{Department of Atomic Energy, Government of India}, has an active research program in many areas of Astronomy and Astrophysics. NCRA has built and operates the Giant Metrewave Radio Telescope, which is located near Pune, and is the most powerful radio telescope in the world at low radio frequencies.\newline{}\newline{}%
{\color{bluecolor}{\large Project Description}}\newline{}
Development of web applications using Free and OpenSource Software (FOSS) and provide system administration to support GMRT (Giant Meterwave Radio Telescope) observations and analysis. Providing maintenance to NCRA Proposal and Archival Management System.\newline{}\newline{}
{\color{bluecolor}{\large Responsibilities}}
\begin{itemize}%
\item Developing and supporting web application for \textbf{Giant Metrewave Radio Telescope Online Archive - GOA} and \textbf{NCRA Proposal Management System} for intake, short listing and Management of various types of Radio Telescope observations at NCRA-TIFR, GMRT, Pune on a reusable framework using Java, J2EE, Hibernate, Python, Shell Scripting and YUI.
\item Developed with the Sky Map using Google maps API to identify the sources which were identified by the Optical telescope with the available sources in GMRT Online Archive.
\item Working with various image processing libraries for \textbf{building pipeline of automated creation of JPEG images} from astronomical FITS images and integrating with GMRT Online Archives System for giving a rough idea to astronomers how the source looks like.
\item Working on further developing, maintaining and enhancing the capabilities of existing \textbf{NCRA Proposal System} and \textbf{GMRT Online archiving} web application.
%\item \textbf{Upgrading of NCRA's new website} based on top of Plone 5 which is configured according to the needs of NCRA-TIFR with required add-on packages and external Database like MySQL and integrated with LDAP authentication.
\item Working on System configuration, administration, automation of various backend processes using Python, Shell Scripting.
\item Providing maintenance of various implemented projects for all NCRA academic and scientific programs running on Linux servers.
\end{itemize}}
\vspace{2ex}

\subsection{Freelancing}
\cventrylong{May 2015--Aug 2015}{Freelancer}{Visakhapatnam}{Bangalore}{}{\begin{changemargin}{2.5cm}{0.0cm} \vspace{-7ex} Worked individually for Startup companies Etikkopaka and Anti Bakasur Brigade.
\end{changemargin}
\begin{cvitemize}
\item Extensively worked on \textbf{Java, Android, PHP, MySQL, Python, Shell Scripting, Ajax, JQuery and Bootstrap}.
\item Worked on Raspberry PI v2 Project - For remotely viewing the drive for a based sports car company.
\item Developed web applications in FuelPHP, NodeJS and Android for controlling the
Raspberry PI remotely.
\item Designed & Developed GUI for PI display using TkInter in Python.
\item Designed and developed eCommerce website in Wordpress using Woo Com-
merce for a local handicrafts organization.
\end{cvitemize}}
~\\

\subsection{IDEA Bubbles Pvt. Ltd.}
\cventrylong{Jan 2015 --May 2015}{Software Engineer}{Idea Bubbles}{Bangalore}{}
\newline{}
{\begin{changemargin}{2.5cm}{0.0cm} \vspace{-7ex} Idea Bubbles provides General Health Software Solutions. The company provides end to end solutions for Doctors, Medicos & Nurses.  Develops and maintains the Health Care Sectors Web and mobile applications.\newline{}\newline{}%
~\\
{\color{bluecolor}{\large Project Description}}\newline{}
Worked on further developing and enhancing the capabilities of Idea Bubbles's products on its core, user interface and other aspects and its maintenance.\newline{}\newline{}
{\color{bluecolor}{\large Responsibilities}}\end{changemargin}
\begin{cvitemize}%
\item Extensively worked on \textbf{ PHP, Android, Parse NoSQL, Amazon Web Services, MySQL, Python, Shell Scripting, Ajax, JQuery and Bootstrap}.
\item Developed the API in Parse PHP SDK for Android app request handling.
\item Designed & developed admin management console for a Android based health
care app in Laravel PHP framework. 
\item Installation and configuring AWS server and deploying the applications.
\item Configuring the Video calls and SMS automatic texts to the clients/mobile
app users, using UMS Technologies package.
\item Installing and configuring the Parse No-SQL online backed. 
\end{cvitemize}}

~\\


\subsection{Alternative Analysis and Risk Management Corp Ltd.}
\cventrylong{May 2013 --December 2014}{Software Engineer}{AARM Corp}{Visakhapatnam}{}{\begin{changemargin}{2.5cm}{0.0cm} \vspace{-7ex} Alternative Analysis and Risk Management Pvt. Ltd. is the Subsidiary of Alternative Assets and Risk Management LLC , Boston MA. This company provides the reports for Private Equity management and investment solution. This particular branch in INDIA is the backend data management and report generation management resource. \newline{}\newline{}%
~\\
{\color{bluecolor}{\large Project Description}}\newline{}
Worked on UNIX scripting and PL/SQL MySQL scripts and Ruby on Rails projects deployment, .\newline{}\newline{}
{\color{bluecolor}{\large Responsibilities}}\end{changemargin}
\begin{cvitemize}%
\item Extensively worked on \textbf{Java, MySQL, Shell Scripting}.
\item Worked on implementing the SQL and PL/SQL for generating client reports.
\item Installing and configuration of Ubuntu servers and deploying the companies Ruby on Rails web application. 
\item Database syncing and merging, build tools to check the Quality of dat in database using UNIX Scripting.
\item Build various tools for office utilities (Salary Management Tool).
\end{cvitemize}}

~\\
~\\
~\\
\section{Personal Details}
\cvitem{Date of Birth}{19-August-1992}
\cvitem{Nationality}{Indian}
\cvitem{Gender}{Male}
\cvitem{Passport No.}{K6571369}
\cvitem{Languages}{English, Hindi, Telugu}
\cvitem{Permanent Address}{Ganesh Nilayam, Taraka Ram Nagar, Behind RTC Complex, Pithapuram, East Godavari, Andhra Pradesh, INDIA}
\cvitem{Hobbies}{ Trekking, Driving, Cooking, Electronic Gadgets, Visiting Places, Sci-Fi Movies.}

~\\

\section{Declaration}
All the information furnished above is true to the best of my knowledge and belief.

~\\
~\\
~\\
~\\
\begin{flushleft}
{\color{bluecolor}{\large Place : Pune}} ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\ ~\  {\color{bluecolor}{\large Bollapragada Naga Ratna Kumar}}
\end{flushleft}


% $\pi$ $=$ $\phi$
% $\hbar$

%Albert Einstein discovered that $e=mc^2$ in 1905.
%\[ e=\lim_{n \to \infty} \left(1+\frac{1}{n}\right)^n \]

\end{document}
